Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-09-28 SubGenome Analysis.Rmd
Working on proteins

@@

```{r subgenome_expression_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=4, fig.align='center'}
plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 1, TRUE)
# plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 4, FALSE)
plot(plot)
```

>>>>

Protein abundance data was retrieved from [Walley 2016](http://science.sciencemag.org/content/353/6301/814.full) supplamental table S2. This dataset contains 3 to 7 biological replicates over 33 tissues.  Expression data is based on a subset of this protein data tissues. Values are in dNASF, which is summarized [here](http://research.stowers.org/proteomics/Quant.html).

@@

```{r subgenome_expression_dominance, echo=FALSE, warning=FALSE, message=FALSE, results='hide', fig.width=10, fig.height=6, fig.align='center'}
# plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 1, TRUE)
# plot <- graphGenePairExpressionsByExperiement(maize.expression.all, homeologs.pairs, 2:12, 4, FALSE)
plot <- graphGenePairExpressionsByExperiement(maize.expression.sample.avg, homeologs.pairs, 2, TRUE)
plot(plot)
```
